A back of the envelope analysis of egg production at 339 Davyhulme Road
========================================================

I got a swing set for my sixth birthday. It was blue and red with yellow swings and a hanging see-saw. Everyone wanted to be my friend because I had the best swing set. One sad day, a mere 22 years after my sixth birthday, my swing set disappeared. It was repleaced by a massive compound for 4 chickens.

The purpose of this document is to quantify the **costs** (_financial, environmental, temporal, emotional_) of domestic egg production from chickens.

All data are reliably (_read:_ unreliably) provided by the stakeholders of the experiment (_i.e._ my parents, who from here on will be known as the **mothership** and the **fathership**).

## How much stuff to make one egg

There are

    4 chickens

who were obtained

    7 months ago

they started laying after 

    4 months of no egg production

and are expected to lay for

    68 months.

They are located at 339 Davyhulme Road (the natural habitat of the Hemani family).

Since they were acquired the **mothership** asserts that the amount of food that has been bought _specifically for the chickens_ is

 - 20kg of corn feed (of which 15kg remains)
 - 65kg of Stephensons Animal Feeds Ltd "Poultry Feed" (of which 20kg remains)

so in total 

    50kg of feed has been consumed by 4 chickens over 7 months.

Due to inadequate record keeping, it is unknown how feed intake has changed over time. The chickens have been laying for 3 months and are now fully grown, so I will assume that

    20kg were consumed over the first 4 developmental months

and

    30kg over the last 3 egg-laying months.

Therefore, as one egg is provided by each chicken each day, 

    30kg / 4 chickens / (3 x 30 days) = 83g of feed

is required to make one egg.

In addition, the chickens consume kitchen waste (again, inadequate record keeping means we cannot quantify this), and they walk around the garden eating stuff that they find tasty (like worms).

This estimate of chicken feed is consistent with this study:

[http://www.lrrd.org/lrrd4/3/bangla1.htm][0]

which claims 114g of feed is required to produce one egg.



## Food waste


## Browsing




```{r}

```

You can also embed plots, for example:

```{r fig.width=7, fig.height=6}

```


[0]: http://www.lrrd.org/lrrd4/3/bangla1.htm